Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-16 Scripts/Initial_Analysis.Rmd
Modified function to see if it uses less memory

@@

@@

@@

@@

@@

@@

data_type <- "catch"
ensamble_list <- seq(102,103,1)
world_grid <- tibble(index = seq(1,259200,1))
path = DBEM_path

@@

spp_list <- unique(Transboundary_spp$taxon_key)

@@

#### Emerging Routine
```{r Emerging_routine, eval = F, echo = F}

@@

spp_list <- c(600004,
              600005,
              600245,
              600006
              )

@@

suppressMessages(
  suppressWarnings(
    Test <- bind_rows(
      mclapply(spp_list,
             TransIndex,
             year,
             data_type = "Catch",
             ensamble_list,
             path,
             Neighbours,
             eez_centroid
      )
    )
  )
)

@@

@@

>>>>

#### Fun `GetCentroids`

```{r GetCentroids, eval = F, echo = T}

GetCentroids <- function(taxon_key,year, data_type = "Catch", ensamble, path, Neighbours, eez_centroid){

@@

  # Get model data from spps
  Spp_Dist <- dbem_import(
    taxon_key = taxon_key,
    year = year,
    data_type = "Catch",
    ensamble = ensamble,
    path = path
  )

@@

  suppressMessages(
    spp_df <- read_csv("~/Desktop/spp_df.csv")
  )
  spp_df <- tibble(taxon_key,
                   ensamble) %>% 
    bind_rows(spp_df) %>% 
    write_csv(.,
              "~/Desktop/spp_df.csv")

@@

    # Get the centroid of each country
    EEZ_centroid <- eez_centroid %>% 
      filter(eez_name %in% Trans_Spp$eez_name) %>% 
      mutate(taxon_key = taxon_key)

    CentroidsFx <- function(Ids){

@@

      return(Distance_Data)

    Centroids_Data <- bind_rows(
      lapply(Ids,CentroidsFx)
    )

    Centroids_Data <- tibble()

  return(Centroids_Data)

TransIndex <- function(Centroids,Ids){

  Centroids_id <- Centroids %>% 
    filter(neighbour_id %in% Ids)

  EEZ_ids <- Neighbours %>% 
    filter(neighbour_id %in% Ids)

  # Historical mean and sd of distance
  historical <- Centroids_id %>%
    filter(year <= 2000) %>% 
    ungroup() %>%
    group_by(taxon_key,ensamble,eez_name,neighbour_id) %>%
    summarise_at(vars("distance"),
                 c(hd_temp_mean=mean,
                   hd_temp_sd=sd)
    )

  # Future results
  future <- Centroids_id %>% 
    filter(year > 2000)

  # Transboundary Index
  Trans_index <- Centroids_id %>% 
    left_join(historical,
              by = c("taxon_key","eez_name","ensamble","neighbour_id")
    ) %>%
    # Re arrenging table for mutate
    gather("variable","value",distance:hd_temp_sd) %>%
    ungroup()

  Unique_EEZs <- unique(Trans_index$eez_name)

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    group_by(taxon_key,ensamble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensamble,trans_index,RMean)

@@

  return(Final_Result)
}

# test <- bind_rows(
#   lapply(ensamble_list,
#          GetCentroids,
#          taxon_key = 600245,
#          year = year,
#          data_type = "Catch",
#          path = path,
#          Neighbours = Neighbours,
#          eez_centroid = eez_centroid)
# )
# 
# 
#   TransIndex(test,819)
#   
#   bind_rows(
#   lapply(Ids,
#          TransIndex,
#          Centroid = test)
#   )

#### Fun `GetTransIndex`

```{r GetTransIndex, eval = F, echo = T}

GetTransIndex <- function(taxon_key,
                            year,
                            data_type = "Catch",
                            path,
                            ensamble_list,
                            Neighbours,
                            eez_centroid){

    # First step
    # Call Get centroids fucntion for centroids data per ensamble
    Step_one <- bind_rows(
      lapply(ensamble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year,
             data_type = "Catch",
             path = path,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid)
    )

    Ids <- unique(Step_one$neighbour_id)

    # Second Step
    # Get the transboudary index based on all centroids
    Step_two <- bind_rows(
      lapply(Ids,
             TransIndex,
             Centroid = Step_one)
    )

    return(Step_two)
  }

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensamble_list = ensamble_list,
  #   year = year,
  #   data_type = "Catch",
  #   path = path,
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )
  # 
  # 
  # spp_list <- c(600004, 600245)
  # 
  #  test <- bind_rows(
  #   lapply(spp_list,
  #          GetTransIndex,
  #          year = year,
  #          data_type = "Catch",
  #          path = path,
  #          Neighbours = Neighbours,
  #          eez_centroid = eez_centroid,
  #          ensamble_list = ensamble_list
  #   )
  # )
  #

@@

data_type <- "catch"
# ensamble_list <- seq(102,103,1)
ensamble_list <- seq(102,111,1)

world_grid <- tibble(index = seq(1,259200,1))
path = DBEM_path

@@

spp_list <- unique(Transboundary_spp$taxon_key)[1:2]

@@

#### Emerging Routine

```{r Emerging_routine, eval = F, echo = F}

@@

@@

suppressMessages(
  suppressWarnings(
    Test <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year,
               data_type = "Catch",
               ensamble_list = ensamble_list,
               path = path,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

write_csv(Test,
          "~/Desktop/Test.csv")

@@

# Old Code
